### 2014-01-31 analysis/Outline.rmd
smatr messages gone

```{r echo=FALSE, message=FALSE, warning=FALSE}
source("../R/fillDerivedVariables.R")
source("../R/import.R")
library(gplots)
library(scales)
library(magicaxis)

@@

sm <- lapply(split(dfr, dfr$pft), function(x){
      sma(log10(m.rf) ~ log10(m.lf)*dataset_species, 
           data=x)
      })

@@

sm <- lapply(split(dfr, dfr$pft), function(x){
      sma(log10(m.lf) ~ log10(m.so)*dataset_species, 
           data=x)
      })

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
if(packageVersion("smatr") < "3.4-4")
  stop("Please update smatr! We use the new quiet argument.")
source("../R/fillDerivedVariables.R")
source("../R/import.R")
library(gplots)
library(scales)
library(magicaxis)

@@

sm <- lapply(split(dfr, dfr$pft), function(x){
      sma(log10(m.rf) ~ log10(m.lf)*dataset_species, quiet=TRUE,
           data=x)
      })

@@

sm <- lapply(split(dfr, dfr$pft), function(x){
      sma(log10(m.lf) ~ log10(m.so)*dataset_species, quiet=TRUE,
           data=x)
      })
